Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-01 MSc-dissertation.tex
Fig fix

\caption[Mean of the observed data]%
{Mean of the observed data for neutrophil $N$, macrophage $\Phi$, il-1$\beta$ and tnf-$\alpha$, from experiment results of \cite{ref:Tsarouchas}. Error bars indicate standard error of mean} 
\label{fig:obs_data}

@@

    \caption[Synthetic data generated with known parameter values]%
    {Synthetic data generated with known parameter values (line plot), compared to experimental data (scatter plot)} 
    \label{fig:infer_back_data}

@@

Among them the following topics are studied using synthetic data.

>>>>

\caption[Mean of the observed data]%
{Mean of the observed data for neutrophil ($N$), macrophage ($\Phi$), il-1$\beta$ and tnf-$\alpha$, from experiment results of \cite{ref:Tsarouchas}. Error bars indicate standard error of mean} 
\label{fig:obs_data}

@@

    \caption[Synthetic data generated with known parameter values]%
    {Synthetic data generated with known parameter values (line plot), compared to experimental data (scatter plot). Known parameter values are obtained from a least square fitting of the observed data} 
    \label{fig:infer_back_data}

@@

[TABLE for known parameter values]

[why use synthetic data]

Among them the following topics are studied using the synthetic data.
